Capon Beamforming Applied on Moving Objects - An Analysis of Local Shift-Invariance

### 2013-10-31 HRUIofMovingObjects/jrnl_article.tex

\section{Local Shift Invariance of the Capon Beamformer}
We will now investigate the lateral local shift-invariance of the Capon beamformer with parameters equal to the once used in earlier work \comment{cite}. A  . Fig.\,\ref{fig:capon1}.

@@

@@

\section{Oversampling by Phase Rotation}
The Capon beamformer formula in (\ref{eq:capon_weights}) gives a direct opportunity for oversampling using phase rotation. The steering vector $\vec{a}$ has previously been set to $\vec{1}$ since the data are pre-delayed, but it could be varied over a set of pre-defined steering vectors. \comment{Look at the poster for notation}

@@

\section{Oversampling by Parallel Receive Lines}
In (\comment{Cite paper where they use STB + Capon if its out}) it is shown that  synthetic transmit beamforming (STB) \cite{Hergum2007} works with Capon beamforming. In  \cite{Asen} we also used STB in order to increase the beam density of a cardiac recording. STB has been shown to remove the blocky artifacts introduced by parallel receive lines (PRL) per transmit line. As long as some degree of motion compensation is applied (\comment{cite bastien's paper on motion compensation }) we can regard PRL as being equal to oversampling on transmit. It will also increase the number of covariance matrices, and thereby inversions with a factor equal to the number of parallel lines.
%\begin{figure}[!t]
%	\centering
%	\includegraphics[width=\linewidth]{\img capon_L=32_K=1_d=001_2MLA_and_2x_microsteering_correct_pitch.eps}
%	\label{fig:image_capon_bs}
%\end{figure}

\section{In-vitro Images}
Acquire channel data from a phantom containing point wire targets and cysts while moving the probe laterally. Confirm the improved shift-invariance when using phase rotation. See if improved sampling also increase cyst contrast.

\section{In-Vivo Images}
Investigate if phase rotation improves contrast in in-vivo images of the heart.

\section{Results}\label{sec:res}
Make plot of contrast between two areas in a simulation for different values of $L$. Make the same plot for different number of rx beams. Do the same for an in-vivo image. The rational being that contrast is also improved by denser rx-sampling not just shift-invariance.

>>>>

\section{Local Lateral Shift-Invariance of the Capon Beamformer}
We will now investigate the lateral local shift-invariance of the Capon beamformer with parameters equal to the once used in earlier work \comment{cite}. A  . Fig.\,\ref{fig:capon1}.

@@

\section{Methods}

@@

\subsection{Oversampling by Phase Rotation}
The Capon beamformer formula in (\ref{eq:capon_weights}) gives a direct opportunity for oversampling using phase rotation. The steering vector $\vec{a}$ has previously been set to $\vec{1}$ since the data are pre-delayed, but it could be varied over a set of pre-defined steering vectors. \comment{Look at the poster for notation}

@@

\subsection{Oversampling by Parallel Recieve Lines}
In (\comment{Cite paper where they use STB + Capon if its out}) it is shown that  synthetic transmit beamforming (STB) \cite{Hergum2007} works with Capon beamforming. In  \cite{Asen} we also used STB in order to increase the beam density of a cardiac recording. STB has been shown to remove the blocky artifacts introduced by parallel receive lines (PRL) per transmit line. As long as some degree of motion compensation is applied (\comment{cite bastien's paper on motion compensation }) we can regard PRL as being equal to oversampling on transmit. It will also increase the number of covariance matrices, and thereby inversions with a factor equal to the number of parallel lines.
%\begin{figure}[!t]
%	\centering
%	\includegraphics[width=\linewidth]{\img capon_L=32_K=1_d=001_2MLA_and_2x_microsteering_correct_pitch.eps}
%	\label{fig:image_capon_bs}
%\end{figure}

\section{Results}\label{sec:res}

Acquire channel data from a phantom containing point wire targets and cysts while moving the probe laterally. Confirm the improved shift-invariance when using phase rotation. See if improved sampling also increase cyst contrast.
Make plot of contrast between two areas in a simulation for different values of $L$. Make the same plot for different number of rx beams. Do the same for an in-vivo image. The rational being that contrast is also improved by denser rx-sampling not just shift-invariance.

\subsection{In-vitro Images}
Acquire channel data from a phantom containing point wire targets and cysts while moving the probe laterally. Confirm the improved shift-invariance when using phase rotation.

\subsection{In-Vivo Images}
Investigate if phase rotation improves contrast in in-vivo images of the heart.
